A large-scale analysis of racial disparities in police stops across the United

### 2019-12-10 lib/paper_results.Rmd
paper updates before outcome test change to get p-values

State search p-values:
`r slice(pstate, 1:2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, 1:2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pstate, -2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, -2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pstate, 2:3) %>% select(agency, subject_race) %>% kable()`
p-value:`r slice(pstate, 2:3) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, 1:2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, 1:2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, -2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, -2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, 2:3) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, 2:3) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`

@@

@@

```{r disparity-state-hit_rates-plot, fig.height=6, fig.width=10}
axis_min <- max(
  min(
    disp$state$outcome$plots$aggregate$data$minority_rate,
    disp$state$outcome$plots$aggregate$data$majority_rate
  ) - 0.05, 0
)
axis_max <- min(
  max(
    disp$state$outcome$plots$aggregate$data$minority_rate,
    disp$state$outcome$plots$aggregate$data$majority_rate
  ), 1
)
disp$state$outcome$plots$aggregate + 
  theme(
    legend.position = "none",
    plot.title = element_blank()
  ) +
  scale_x_continuous(
    limits = c(axis_min, axis_max),
    labels = scales::percent_format(accuracy = 1), expand = c(0,0)
  ) + 
  scale_y_continuous(
    limits = c(axis_min, axis_max),
    labels = scales::percent_format(accuracy = 1),expand = c(0,0)
  ) 
```

@@

```{r disparity-state-thresholds-plot, fig.height=5, fig.width=10}
disp$state$threshold$prior_scaling_factor_1$plots$aggregate + 
  theme(
    legend.position = "none",
    plot.title = element_blank()
  )
```

>>>>

Search p-values:
`r slice(pstate, 1:2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, 1:2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pstate, -2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, -2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pstate, 2:3) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, 2:3) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, 1:2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, 1:2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, -2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, -2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, 2:3) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, 2:3) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`

@@

Hit rate p-values:
`r slice(pstate, 1:2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, 1:2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pstate, -2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, -2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pstate, 2:3) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pstate, 2:3) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, 1:2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, 1:2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, -2) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, -2) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`
`r slice(pcity, 2:3) %>% select(agency, subject_race) %>% kable()`
p-value: `r slice(pcity, 2:3) %>% select(n_success, n_failure) %>% as.matrix %>% prop.test %$% p.value`

@@

```{r disparity-state-hit_rates-plot, fig.height=6, fig.width=10}
disp$state$outcome$plots$aggregate + theme(legend.position = "none")
```

@@

```{r disparity-state-thresholds-plot, fig.height=5, fig.width=10}
disp$state$threshold$prior_scaling_factor_1$plots$aggregate + theme(legend.position = "none")
```
